Delocalization of Eigenvectors in Random Matrices

### 2025-03-20 Draft.tex
typos

$$\partial_{t}\{\text{Id}+(t-s)\Theta_t\} = \Theta_t+(t-s)\Theta_t^2=\Theta_t\frac{1-t|m(z)|^2S+(t-s)|m(z)|^2S}{1-t|m(z)|^2S}=$$
$$=\Theta_t \frac{1-s|m(z)|^2S}{1-t|m(z)|^2S}=\Theta_t\{\text{Id}+(t-s)\Theta_t\}$$
Let $\mathcal{E}_t(z)$ be the fluctuation term, i.e the difference between our $T$-matrix and the diffusion profile:
$$\E_t(z):T_t(z)-\Theta_t$$
Let us compute its evolution equation $d\E_t(z) = dT_t(z)-d\Theta_t$ by substituting for what we found before:
$$\Rightarrow d\E_t(z) = T_t(z)^2dt + \Theta_t^2dt-S^{1/2}dM_t(z)S^{1/2}+S^{1/2}\Omega_t(z)S^{1/2}dt$$
But observe that:
$$T_t(z)^2-\Theta_t^2 =(\E_t(z)+\Theta_t(z))^2- \Theta_t(z)^2=\E_t(z)^2+\Theta_t\E_t(z)+\E_t(z)\Theta_t$$

 $$\Rightarrow d\E_t(z)=\{\Theta_t \E_t(z)+\E_t(z)\Theta_t\}dt +\E_t^2(z)dt - S^{1/2} dM_t(z)S^{1/2} + S^{1/2} \Omega_t(z) S^{1/2}dt$$
Integrating $\E_t(z)$ over $s$:
$$\E_t(z)=\int_0^t \{\text{Id} + (t-s)\Theta_t\}\left\{\E^2(s)ds +S^{1/2} dM(s)S^{1/2}+  S^{1/2} \Omega(s) S^{1/2}\right\} \{\text{Id} + (t-s)\Theta_t\}ds,$$
whereas we can split the terms in three separate components, each of which we will individually bound in the following section:

$$\E_t^{D}(z)=\int_0^t \{\text{Id} + (t-s)\Theta_t\} S^{1/2} \Omega(s) S^{1/2} \{\text{Id} + (t-s)\Theta_t\}ds,$$
$$\E_t^{M}(z)=\int_0^t \{\text{Id} + (t-s)\Theta_t\}S^{1/2} dM(s)S^{1/2}+ \{\text{Id} + (t-s)\Theta_t\}ds,$$
$$\E_t^{S}(z)=\int_0^t \{\text{Id} + (t-s)\Theta_t\}\E_s^2(z) \{\text{Id} + (t-s)\Theta_t\}ds,$$

@@

$$\int_0^t \{\text{Id} + (t-s)\Theta_t\} S^{1/2}dM(s)S^{1/2} \{\text{Id} + (t-s)\Theta_t\}= $$$$=\int_0^t \{\text{Id} + (t-s)\Theta_t\}\sum_{u, v}\left[\overline{G_{xy}}G_{xu}dH_{uv}(t)G_{vy}\right]\{\text{Id} + (t-s)\Theta_t\}+$$
$$+ \int_0^t \{\text{Id} + (t-s)\Theta_t\}\sum_{u, v}\left[G_{xy}\overline{G_{xu}dH_{uv}(t)}\overline{G_{vy}}\right]\{\text{Id} + (t-s)\Theta_t\}$$

>>>>

$$\partial_{t}\{\text{Id}+(t-s)\Theta_t\} = \Theta_t+(t-s)\Theta_t^2=\Theta_t\frac{1-t|m(z)|^2S+(t-s)|m(z)|^2S}{1-t|m(z)|^2S}=$$
$$=\Theta_t \frac{1-s|m(z)|^2S}{1-t|m(z)|^2S}=\Theta_t\{\text{Id}+(t-s)\Theta_t\}$$
Let $\mathcal{E}_t(z)$ be the fluctuation term, i.e the difference between our $T$-matrix and the diffusion profile:
$$\E_t(z):T_t(z)-\Theta_t$$
Let us compute its evolution equation $d\E_t(z) = dT_t(z)-d\Theta_t$ by substituting for what we found before:
$$\Rightarrow d\E_t(z) = T_t(z)^2dt - \Theta_t^2dt-S^{1/2}dM_t(z)S^{1/2}+S^{1/2}\Omega_t(z)S^{1/2}dt$$
But observe that:
$$T_t(z)^2-\Theta_t^2 =(\E_t(z)+\Theta_t(z))^2- \Theta_t(z)^2=\E_t(z)^2+\Theta_t\E_t(z)+\E_t(z)\Theta_t$$

 $$\Rightarrow d\E_t(z)=\{\Theta_t \E_t(z)+\E_t(z)\Theta_t\}dt +\E_t^2(z)dt - S^{1/2} dM_t(z)S^{1/2} + S^{1/2} \Omega_t(z) S^{1/2}dt$$
\textcolor{red}{Integrating $\E_t(z)$ over $s$}:
$$\E_t(z)=\int_0^t \{\text{Id} + (t-s)\Theta_t\}\left\{\E^2(_sz)ds -S^{1/2} dM(s)S^{1/2}+  S^{1/2} \Omega(s) S^{1/2}\right\} \{\text{Id} + (t-s)\Theta_t\}ds,$$
whereas we can split the terms in three separate components, each of which we will individually bound in the following section:

$$\E_t^{D}(z)=\int_0^t \{\text{Id} + (t-s)\Theta_t\} S^{1/2} \Omega(s) S^{1/2} \{\text{Id} + (t-s)\Theta_t\}ds,$$
$$\E_t^{M}(z)=-\int_0^t \{\text{Id} + (t-s)\Theta_t\}S^{1/2} dM(s)S^{1/2}\{\text{Id} +(t-s)\Theta_t\}ds,$$
$$\E_t^{S}(z)=\int_0^t \{\text{Id} + (t-s)\Theta_t\}\E_s^2(z) \{\text{Id} + (t-s)\Theta_t\}ds,$$

@@

$$\int_0^{t\wedge \tau_\sto} \{\text{Id} + (t-s)\Theta_t\} S^{1/2}dM(s)S^{1/2} \{\text{Id} + (t-s)\Theta_t\}= $$$$=\int_0^{t\wedge \tau_\sto} \{\text{Id} + (t-s)\Theta_t\}\sum_{u, v}\left[\overline{G_{xy}}G_{xu}dH_{uv}(t)G_{vy}\right]\{\text{Id} + (t-s)\Theta_t\}+$$
$$+ \int_0^{t\wedge \tau_\sto} \{\text{Id} + (t-s)\Theta_t\}\sum_{u, v}\left[G_{xy}\overline{G_{xu}dH_{uv}(t)}\overline{G_{vy}}\right]\{\text{Id} + (t-s)\Theta_t\}$$
